---
title: "Precision and Recall"
date: "`r paste0('Last Updated: ', format(Sys.time(), '%d %B, %Y')) `"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
editor_options: 
  chunk_output_type: console
---

# Prompt

Each user can have multiple sessions. Write a SQL query that:
- selects the ‘userIds’ with the top 50 average session durations
- selects their full name from the user table as a single new column
*Bonus for adding in a new column for each user and flagging their 3rd longest duration with 1,
otherwise put 0 (put 0 if they have fewer than 3 sessions)


```{r setup, include = F}
knitr::opts_chunk$set(echo = T, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.align = 'center')

library(tidyverse)
library(sqldf)
# To Turn off Scientific Notation Use this.
options(scipen = 999)
```

# Build Tables
To help with future potential troubleshooting, I have created small and simple tables to allow us to run the queries against.

## Building User Table
```{r, eval=F}

users <- data.frame(
  id = seq(1:10), 
  firstName= stringi::stri_rand_strings(10, 5, '[a-z]'), 
  lastName = stringi::stri_rand_strings(10, 2, '[A-Z]')
) 

save(users, file = here::here("data", "users.rds"))
```


## Building Sessions Table
```{r, eval=F}
sampleUser <- sample(users$id, 100, replace= T) 
sampleDur <- sample(10:50, 100, replace=TRUE)

sessions <- data.frame(
  id = seq(1:100),
  userId = sampleUser,
  duration = sampleDur
)
  
save(sessions, file = here::here("data", "sessions.rds"))
```



## Building Transactions Table
```{r, eval=F}
records <- 200

sampleUserTXN <- sample(users$id, records, replace= T) 
sampleProd <- sample(111:120, records, replace=TRUE)
sampleOrigDT <- sample(1900:2020, records, replace=TRUE)
sampleQTY <- sample(1:10, records, replace=TRUE)

transactions <-  data.frame(
  id = seq(1:records),
  userId = sampleUserTXN,
  productId = sampleProd,
  originDate = sampleOrigDT,
  description = "",
  qty = sampleQTY
)

save(transactions, file = here::here("data", "transactions.rds"))
```


## Load Tables (that would be in DB)
```{r}
load(file = here::here("data", "users.rds"))
load(file = here::here("data", "sessions.rds"))
load(file = here::here("data", "transactions.rds"))
```

# Top Avg Durations and New Name Column

I just created sample tables with 10 different users. If the tables were larger it would have pulled more records (or we could expand with further by changing the where statement to be '<= 50')

Used a CTE to create a summary table, which I then used to query against.

```{r}

sqldf("
with avgDur (userID, AvgDur, ranking) as (
  select userId, avg(duration) as AvgDur, RANK() OVER (ORDER BY avg(duration) DESC) as ranking
  from sessions
  group by UserId
  order by 2 desc)

select firstName ||' '|| lastName as Combined_name, AvgDur, ranking
from avgDur avg left join 
users u on u.id = avg.userID
where ranking <= 5

")


```

# Flag the 3rd longer duration per user

Using a windowing function to rank the durations by userid.

Showing below an example of userID 2
```{r}

sqldf("
with rankDur (userID, duration, ranking) as (
  select userId, duration, DENSE_RANK() OVER(PARTITION BY userId ORDER BY duration DESC) as ranking
  from sessions)
      
select *, case when ranking = 3 then 1 else 0 end as FlagThird
from rankDur
where userID = 2
")


```


